---
title: "dogetweet"
author: "Ivan Cherniavskyi"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This package is creating data frame which includes information about desired 
crypto currencies provided by [CoinMarketCap](https://coinmarketcap.com/), as well 
as conversation volume markers in various social media.

## Install

Install from GitHub with the following code:

```{r install, eval = FALSE}
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}
devtools::install_github("icherniavsky/dogetweet")
```

This package connects <code>dogetweet</code> to <code>rtweet</code>, 
<code>gtrendsR</code>, <code>RedditExtractoR</code> and <code>coinmarketcapr</code>. 

As a result, each user must have previously acquired Basic API Key from 
CoinMarketCap which can be found by following this [link](https://coinmarketcap.com/api/). 

Additionally, each user must have twitter account for <code>rtweet</code> to work. 
At the first start of <code>dogetweet</code>, <code>rtweet</code> will connect 
you to Twitter API automatically in a new window of your browser. Be aware that 
the function <code>stream_tweets</code> has some restrictions. 
More information about the restricitions can be found 
[here](https://developer.twitter.com/en/docs/twitter-api/v1/tweets/filter-realtime/guides/streaming-message-types).

## Usage

There are three functions currently live for dogetweet. 

To begin, the user must first enter the following code, inserting their key:

```{setup instructions, eval = FALSE}
api_setup("YourAPIKey")
```

Currently, this must be done at the start of every session.

The next function <code>crypto_names</code> is designed to provide the user with
all crypto currencies available for usage with <code>dogetweet</code>.

```{cryoto_names, eval = FALSE}
crypto_names(name = "crypto_list")

crypto_names(crypto_list)

Example of the crypto_list object:

[1] Bitcoin

[2] Euthereum

[3] Binance Coin

[4] XRP

[5] Tether


```

<code>crypto_names</code> has one argument which assigns the chosen name to the 
object with the list of currencies. The default name of the object is crypto_list.

The third and main function is <code>dogetweet</code>. It gathers data from 
CoinMarketCap and three media platforms like Twitter, Reddit and Google Hits. 
The function put the collected data into a data frame in the global environment. 
Additionally, it saves data frame into user's working directory as .RData file. 
The name of data frame/object and .RData file is the same as the name of 
searched crypto currency.

```{dogetweet, eval = FALSE}
dogetweet(crypto = "Dogecoin", timout = 60)
```

The <code>dogetweet</code> function itself has two arguments. 

The first argument is the name of crypto currency to perform search for. 
The default is Dogecoin.   

The next argument determines how long an open stream of tweets will be collected, 
with a default of 60 seconds. Please be aware that <code>rtweet</code> has 
several restriction. It is not recommended to run the function more than 1 time 
per minute or run two searches simultaneously. More information can be found 
[here](https://developer.twitter.com/en/docs/twitter-api/v1/tweets/filter-realtime/guides/streaming-message-types).

The data frame has 12 variables. Name variable is the name of the selected 
crypto currency. USD_last_updated is the time when the price of the currency was 
updated by CoinMarketCap. Sys_time and Sys_date are time and date when the 
function was run by the user. USD_price is the current price of the currency.
Price_change describes the rate of change of the price. Tweets is the number of 
tweets found by streaming. Twitter_change is the rate of change in number of 
tweets. Google_hits is the number of hits in Google regarding the currency.
Google_change describes the rate of change in hits. Reddit_comments shows
the number of comments in Reddit regarding crypto. And reddit_change describes 
the rate of change of Reddit comments.

This process takes some time, as dogetweet is rely on multiple dependencies such 
as Rtweet, RedditExtractoR and gtrendsR which take some time to run. 

